### 2019-02-13 sections/relatedwork.tex
TOP vs FRP

>>>>

\subsection{Functional Reactive Programming}

Functional Reactive Programming (FRP) is a paradigm to describe dynamic changes of values in a declarative way.
This is done by specifying networks of values, called behaviors, that can depend on each other and on external events.
Behaviors can change over time, or triggered by events.
When a behavior changes, all other behaviors that depend on it are updated automatically.
The underlying implementation that takes care of the updating usually can tie input devices, like mouse and keyboard, to event streams and behaviors to output facilities, like text fields.
This allows for declarative specifications of applications with user interfaces.

The idea of FRP was pioneered by \citet{conf/icfp/ElliottH97}, in the meantime there are many variants and implementations, with reactive-banana one of the most well-known \cite{reactive-banana}.

FRP and \TOP are different systems that have different goals in mind.
Whereas FRP expresses automatically updating data dependencies, \TOP expresses collaboration patterns.
\TOP has no notion of time.
Tasks can not change over time, while behaviors can.
The biggest conceptual difference between a workflow in \TOP and a data network in FRP is that an event to a task only causes updates up until the next step, while an event in FRP propagates through the whole network.

That being said, there are some concepts that are similar in \TOP and FRP.
The \emph{stepper} behavior for example is associated with an event and yields the value of the most recent event.
This is similar to editors in \TOP.
Furthermore, both systems can be used to declaratively program user interfaces.
